\documentclass[answers]{exam}
\usepackage{graphicx} % Required for inserting images
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb} % for \square
\usepackage{amsthm}
\usepackage{float}
\usepackage{tikz}
\usetikzlibrary{calc}

\usepackage[en-US,showdow]{datetime2}

\newcommand{\ds}{\displaystyle}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\arc}{\rightarrow}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}

\newcommand{\stirling}[2]{\genfrac{\{}{\}}{0pt}{}{#1}{#2}}

\usepackage{mathtools}
\def\multiset#1#2{\ensuremath{\left(\kern-.3em\left(\genfrac{}{}{0pt}{}{#1}{#2}\right)\kern-.3em\right)}}

\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}

\title{Midterm Adventure}
\author{By: Matt Sorensen\\
James Richardson \\
Aidan Andersen \\
Denzil Rogers}
\date{March 6th, 2026}

\begin{document}
\maketitle



	\section*{Rules of Engagement}
	
	You may discuss the problems below with anyone in the following set of people:
	\begin{eqnarray*}P &=& \{\mbox{Anyone currently enrolled in MATH 3310}, \\ 		&& \mbox{Kaylee Bodily, Caroline Torman, Erin Pitts, Brent Thomas}\}.\end{eqnarray*}
	
    The documentation of your adventure should be created by teams of at most 4 and is to be submitted by \DTMdate{2026-03-06} as a PDF via Canvas (the way we've done all semester). One submission per team.\\
        
    No outside resources are to be used on this experience.
	Try to get through this with your brain and the brains of your team (if you choose to be part of one). \\
	
	
	\section{The Adventure Begins} 
	
	\subsection*{Sneaking into Hogsmeade}
	\qformat{\textbf{Sub-Adventure \thesection.\thequestion }\hfill}
	\begin{questions}
		\question 
		
		Argus Filch and Severus Snape are playing a game in which they try to destroy all secret passages between Hogwarts, Hogsmeade, and the Shrieking Shack. Argus and Severus take turns destroying passages. On their turn, they select a location and destroy any positive number of passages to the other two locations. The winner of the game is the player who is able to destroy all the remaining passages on their turn.

	As an example, suppose there are 2 passages between the Shrieking Shack and Hogwarts, 1 passage between Hogwarts and Hogsmeade, and 3 passages between the Shrieking Shack and Hogsmeade.
		
		\begin{center}
			\begin{tikzpicture}[scale = 1.5]
				\tikzset{vertex/.style = {shape=circle,fill = black, draw, scale = 0.50}}
				
				%\node[] (label_d0) at (-4,0) {$K_1$};
				
				\node[vertex] (A) at (0,0) {};
				\node[] (label_A) at (-0.3,-0.3) {Shrieking Shack};
				\node[vertex] (B) at (2,0) {};
				\node[] (label_B) at (2.3,-0.3) {Hogsmeade};
				\node[vertex] (C) at (1,2) {};
				\node[] (label_C) at (1,2.3) {Hogwarts};
				
				\draw[] (A) to (B) to (C) to [bend right] (A) to [bend right] (B) 
				to [bend right] (A) to (C);
				
			\end{tikzpicture}
		\end{center}
		

		Suppose, in general, there are $x$ passages between the Shrieking Shack and Hogwarts, $y$ passages between Hogwarts and Hogsmeade, and $z$ passages between the Shrieking Shack and Hogsmeade.

		\emph{Determine, with proof, the values of $x,y,z$ for which Severus Snape (the first player) can always win if a particular strategy is employed for each move.}\\
		
		\begin{solution}
			Claim: Player 1 (Snape) has a winning strategy for every starting position in which the number of passages in each side is not equal.


            \begin{proof}
                We can prove this through induction. 

                Let x, y, z = N meaning that all of the routes have the same number of passages. 

                Base Case:
                N = 1

            \begin{tikzpicture}[scale = 1.5]
				\tikzset{vertex/.style = {shape=circle,fill = black, draw, scale = 0.50}}
				
				%\node[] (label_d0) at (-4,0) {$K_1$};
				
				\node[vertex] (A) at (0,0) {};
				\node[] (label_A) at (-0.3,-0.3) {Shrieking Shack};
				\node[vertex] (B) at (2,0) {};
				\node[] (label_B) at (2.3,-0.3) {Hogsmeade};
				\node[vertex] (C) at (1,2) {};
				\node[] (label_C) at (1,2.3) {Hogwarts};
				
				\draw[] (A) to (B) to (C) (A) to (B) 
				to (A) to (C);
				
			\end{tikzpicture}

                In this case the player going first will always lose as long as their opponent understands the game. Player 1 can either remove one passage or 2 in either case player 2 can remove the remaining passages.

                Hypothesis 

                Assume that this is true for N = K + 1 meaning that x + 1, y + 1, z+1 all equal N.

                Inductive step: 
                
                In any of these cases Player 1 can remove from 1 or 2 of the values meaning that Player 2 can match them to create the same position where x y z = N and eventually get to the base case x, y, z = 1

                Therefore any position where x, y, z = N is an unwinable position for the player going first. 

                In any case where x, y, z $\ne$ the winning strategy for player one goes like this. The player finds the side or sides that have the least amount of passageways and removes passageways from the other sides until they match and all sides are equal. This forces player 2 into the same position where x, y, z = N which is unwinnable. 

                Therefore There is a winning strategy for player 1 for every starting position in which the number of passages in each side are not equal.

                
            \end{proof} 

            
		\end{solution}
		
		
		\fullwidth{\subsection*{Dots and Boxes}}
		
		\question
		
		Two players, Link and Zelda, alternately select an \emph{edge} (a line segment connecting two dots) on the grid graph shown 
		below and color it red.
		The loser of the game is the player who is forced to select an edge that creates
		a red $C_4$ --- a red square on $4$ vertices.\\
		
		\begin{center}
			\begin{tikzpicture}[scale = 1]
				\tikzset{vertex/.style = {shape=circle,fill = black, draw, scale = 0.50}}
				\foreach \x in {0,1,2,3,4,5}{
					\foreach \y in {0,1,2,3,4}{
						\node[vertex] (\x\y) at (\x,\y) {};
				}}
				\draw (0,0) grid (5,4);
			\end{tikzpicture}
		\end{center}
		
		
		\noindent \emph{Confirm or deny, with proof, whether Zelda (the first player) can always 
			win if she employs a particular strategy for each move.}
		
		\begin{solution}
        \begin{proof}
        Claim: Zelda will always lose in a 6X5 sized board

        In this game the best strategy is to just connect any edge which does not complete a square. For each C there is 4 sides and so in every case you should only play on $C_0$ $C_1$ and $C_2$ avoiding playing on $C_3$. In other words there is no risk of making a bad move as long as you are not playing on a square which already has 3 connected sides. In every game as long as both players employ this strategy there will be an ending game where every square is left with a $C_3$ and the final player must complete a square and lose. 

        Lemma 1:
        There is always the same amount of edges filled before the final move of the game.

        The final move of the game will always be filling one square in to become $C_4$. This means there are no squares that have less than 3 sides filled in meaning every square must have exactly 3 sides filled in and be $C_3$. If every square is $C_3$ we know that there is always the same amount of edges filled before the final move of the game.

        Lemma 2: 
        
        If the amount of edges is even than the player going first will always win.

        Let E be the number of edges in a game. 
        
        \begin{center}
			\begin{tikzpicture}[scale = 1]
				\tikzset{vertex/.style = {shape=circle,fill = black, draw, scale = 0.50}}
				\foreach \x in {0,1}{
					\foreach \y in {0,1}{
						\node[vertex] (\x\y) at (\x,\y) {};
				}}
				\draw (0,0) grid (1,1);
			\end{tikzpicture}
		\end{center}

        In this case the player going first will always win. The amount of Edges If the shape were a pentagon and E was 5 then it would add one more move before the player was forced to fill in the shape and the next player would win. This means that E + 1 = the player who wins E loses. 
    
        \begin{center}
			\begin{tikzpicture}[scale = 1]
				\tikzset{vertex/.style = {shape=circle,fill = black, draw, scale = 0.50}}
				\foreach \x in {0,1}{
					\foreach \y in {0,1}{
						\node[vertex] (\x\y) at (\x,\y) {};
				}}
				\draw (0,0) grid (2,1);
			\end{tikzpicture}
		\end{center}

        As shown in this example the second player wins because E = 7 which is odd.


        The amount of edges in the given board is 49. This means that E = 49 which is odd meaning that Zelda can never win the game no matter the strategy.

        
        
            
        \end{proof}
			
		\end{solution}
		
		
	\end{questions}
	
	\section{Prime Time}
		\qformat{\textbf{Sub-Adventure \thesection.\thequestion }\hfill}
		\begin{questions}	
			\question Prove or disprove whether you can order the years $2011, \dots, 2026$ so that the resulting $64$-digit number is prime.

			\begin{solution}
			\begin{proof}
		\subsection*{Claim}
		It is not possible to order the years 2011, 2012, \dots, 2026 to form a 64-digit number that is prime. 

		\subsection*{Proof}
		We shall prove this by proving that any such 64-digit number formed by concatenating the years 2011 to 2026 is divisible by 11, and thus composite (Composite means not Prime).

		First we will start by refering to a few things from our notes. According to Theorem 2, part 6, we know that an integer $X$ is divisible by 11 if the alternating sum of its digits, $\sum_{i=0}^{n}(-1)^{i}d_{i}$, is divisible by 11.

		So we will concatinate each year, which which will give us our 64-digit number because we have 16 years and each year has 4 digits. Because each years is just 4 digits, which is an even number of digits, the alternating sum of each year will always be the same, (For example 2011 will always be $1 - 1 + 0 - 2$ no matter where we place it in the 64 digit number). 


		We calculate the individual alternating sums ($d_0 - d_1 + d_2 - d_3$) for each year in the set:

		So here we will calculate the alternating sum for each year:
		\begin{itemize}
			\item 2011: $1 - 1 + 0 - 2 = -2$
			\item 2012: $2 - 1 + 0 - 2 = -1$
			\item 2013: $3 - 1 + 0 - 2 = 0$
			\item 2014: $4 - 1 + 0 - 2 = 1$
			\item 2015: $5 - 1 + 0 - 2 = 2$
			\item 2016: $6 - 1 + 0 - 2 = 3$
			\item 2017: $7 - 1 + 0 - 2 = 4$
			\item 2018: $8 - 1 + 0 - 2 = 5$
			\item 2019: $9 - 1 + 0 - 2 = 6$
			\item 2020: $0 - 2 + 0 - 2 = -4$
			\item 2021: $1 - 2 + 0 - 2 = -3$
			\item 2022: $2 - 2 + 0 - 2 = -2$
			\item 2023: $3 - 2 + 0 - 2 = -1$
			\item 2024: $4 - 2 + 0 - 2 = 0$
			\item 2025: $5 - 2 + 0 - 2 = 1$
			\item 2026: $6 - 2 + 0 - 2 = 2$
		\end{itemize}

		If we add all of those values together we get:
		$$ -2 - 1 + 0 + 1 + 2 + 3 + 4 + 5 + 6 - 4 - 3 - 2 - 1 + 0 + 1 + 2 = 11$$

		Since $11$ is divisible by 11 ($11 = 11 \cdot 1$), then our 64 digit number $X$ is also divisible by 11 based on Theorem 2, part 6.

		By Definition 4 from our notes, 11 is a divisor of $X$, meaning $X = 11k$ for some integer $k$. Since $X$ is a 64-digit number, it is clear that $1 < 11, k < X$. 

		Using our definition of a composite number that we proved in HW 2 Question 1, an integer n is composite if it can be written as $n = st$ where $1 < s, t < n$.

		If we set $n=X$, $s=11$, and $t=k$, we have shown that $X$ meets the criteria for being composite. Therefore, $X$ is not prime by our definition of prime because if something is composite, it is not prime. So, no ordering of the years 2011 to 2026 can result in a prime number.

		\subsection*{Conclusion}
		Thus, we have shown that any 64-digit number formed by concatenating the years 2011 to 2026 is divisible by 11 and therefore composite. Hence, it is not possible to order the years to form a prime number.
					
			\end{proof}
			\end{solution}
			
			
		\end{questions}

		\section{Counting Functions}
			\qformat{\textbf{Sub-Adventure \thesection }\hfill}
			\begin{questions}
			\question If $A$ and $B$ are sets, the notation $B^A$ stands for the set of all functions that map $A$ into $B$.
				Note that $f:A \stackrel{1-1}{\longrightarrow} B$ denotes that $f$ is a function from $A$ into $B$ that is injective.
				Note that $f:A \stackrel{\mbox{onto}}{\longrightarrow} B$ denotes that $f$ is a surjective function mapping $A$ into $B$.
				
				The goal is to count the number of functions with the properties indicated by the row and column headings in the table.
				For example, in entry number $8$ should be the number of functions that are surjective (onto) that map $n$ distinguishable objects to $x$ indistinguishable objects.
				In mathematical notation, this is
				$$\left|\left\{f \in B^A : A=\{a_1,a_2, \dots, a_n\}, |B| = x, f:A \stackrel{\mbox{onto}}{\longrightarrow} B  \right\} \right|.$$
				While entry $6$ should house the number
				$$\left|\left\{f \in B^A : |A|=n, B =\{b_1,b_2, \dots, b_x\}, f:A \stackrel{\mbox{1-1}}{\longrightarrow} B  \right\} \right|.$$
				
				
				\[\begin{array}{c|c||c|c|c}
					\hline A & B & \mbox{unrestricted }& \mbox{onto}& \mbox{injective} \\ \hline \hline
					\mbox{distinguishable} & \mbox{distinguishable} & 1. & 2. & 3. \\ \hline
					\mbox{indistinguishable}& \mbox{distinguishable}&4.&5.&6. \\ \hline
					\mbox{distinguishable} & \mbox{indistinguishable}& 7. & 8. & 9. \\ \hline
					\mbox{indistinguishable}&\mbox{indistinguishable}& 10. &11.&12. \\ \hline 
				\end{array}\]
				
				\noindent Please determine with an argument for each, a formula enumerating the set of functions corresponding to entries 1-12. 
			\end{questions}
		
			\begin{solution}
			\begin{proof}
            
            \begin{enumerate}
                \item 
                    \textbf{Formula:} $x^n$ \\
                    \textbf{Explanation:} 
					To explain this there are $n$ distinguishable objects in $A$ which can be mapped to any of the $x$ distinguishable objects in $B$. Therefore, for each of the $n$ objects, there will always be $x$ choices, we can represent this by our formula $x^n$ because we have $n$ objects and $x$ choices for each object.
                
                \item 
                    \textbf{Formula:} $x! \cdot \stirling{n}{x}$ \\
                    \textbf{Explanation:} 
					To explain this we can think of this as first counting the number of ways to partition the $n$ distinguishable objects in $A$ into $x$ which is just $\stirling{n}{x}$ (As shown by 5) Since we can map $x$ distinguishable objects in $B$ in any order, we multiply by $x!$ to account for all possible orderings we can have.
                
                \item 
                    \textbf{Formula:} $\frac{x!}{(x-n)!}$ \\
                    \textbf{Explanation:} 
					We are counting the number of ways to map $n$ distinguishable objects in $A$ to distinguishable objects in $B$ such that no two objects in $A$ are mapped to the same object in $B$ (The definition of injectivity). This is just the number of ways to choose which $n$ objects in $B$ will be mapped to the $n$ objects in $A$, which is $\frac{x!}{(x-n)!}$ because we are choosing $n$ objects from a set of $x$ objects and the order matters because the objects in $A$ are distinguishable.
                \item 
                    \textbf{Formula:} $\binom{n+x-1}{x-1}$ \\
                    \textbf{Explanation:} 
					We are counting the number of ways to map $n$ indistinguishable objects in $A$ to $x$ distinguishable objects in $B$. This is just the number of ways to partition $n$ indistinguishable objects into $x$ distinguishable boxes, which is $\binom{n+x-1}{x-1}$ we can think of this as placing $n$ indistinguishable balls into $x$ distinguishable boxes. We do the subtraction of 1 from $x$ because we can think of this as placing $n$ indistinguishable balls into $x-1$ distinguishable boxes and then placing the remaining balls in the last box.
                
                \item 
                    \textbf{Formula:} $\stirling{n}{x}$ \\
                    \textbf{Explanation:}
					This is just $\stirling{n}{x}$ because we are counting the number of ways we can partition $n$ indistinguishable objects into $x$ distinguishable boxes. Which is literly it's definition.
                
                \item 
                    \textbf{Formula:} $\binom{n}{x}$ \\
                    \textbf{Explanation:} 
					Since the objects in $A$ are indistinguishable, we just need to choose which $x$ objects in $A$ will be mapped to the $x$ objects in $B$. This is just $\binom{n}{x}$ because we are choosing $x$ objects from a set of $n$ objects.
                
                \item 
                    \textbf{Formula:} $\stirling{n+1}{2}$ \\
                    \textbf{Explanation:} 
					This is just the number of ways to partition $n$ distinguishable objects into $x$ indistinguishable boxes, which is $\stirling{n+1}{2}$ we can think of this as placing $n$ distinguishable balls into $x$ indistinguishable boxes. We do the addition of 1 to $n$ because we can think of this as placing $n$ distinguishable balls into $x-1$ indistinguishable boxes and then placing the remaining balls in the last box.
                
                \item 
                    \textbf{Formula:} $\stirling{n}{x}$ \\
                    \textbf{Explanation:} \
					This is almost exactly the same as 5. Just the indistinguishability of the objects in $A$ does not change the number of ways we can partition them into $x$ distinguishable boxes. So our formula is the exact same as 5 which is $\stirling{n}{x}$.
                
                \item 
                    \textbf{Formula:} $\begin{cases} 1 & \text{if } n \leq x \\ 0 & \text{if } n > x \end{cases}$ \\
                    \textbf{Explanation:} 
					If $n > x$, there are isn't any mappings so we get 0. If $n \leq x$, there is exactly one way to map each object in $A$ to an object in $B$, so we get 1.
                
                \item 
                    \textbf{Formula:}$p_B(A+B)$ \\
                    \textbf{Explanation:} 
					The number of ways to distribute A indistinguishable balls into B indistinguishable boxes is the same thing as partitioning the integer A into at most B parts, a value which simplifies to the formula $p_B(A+B)$.
                
                \item 
                    \textbf{Formula:} $p_B(A)$ \\
                    \textbf{Explanation:} 
					Distributing A indistinguishable balls into B indistinguishable boxes such that every box contains at least one ball is the same thing as finding the number of partitions of the integer A into exactly B parts. So we can use this equasion
                
                \item 
                    \textbf{Formula:} $\begin{cases} 1 & \text{if } n \leq x \\ 0 & \text{if } n > x \end{cases}$ \\
                    \textbf{Explanation:} 
					This is almost the exact same as 9. As we are counting the number of ways to map $n$ indistinguishable objects in $A$ to $x$ indistinguishable objects in $B$. If $n > x$, there are isn't any mappings so we get 0. If $n \leq x$, there is exactly one way to map each object in $A$ to an object in $B$, so we get 1.
            \end{enumerate}
		\end{proof}
            
            \end{solution}
			
	
	\section{Tiling}
		\qformat{\textbf{Sub-Adventure \thesection.\thequestion }\hfill}
		\begin{questions}
			\question Let $T_n$ be the number of ways to perfectly tile a $1 \times n$ floor with $1 \times 1$ and $1 \times 2$ tiles. We say $T_0 =1$ because the tiling with no tiles perfectly tiles a $1 \times 0$ floor.

			\begin{parts}
				\part Give a recursive formula for $T_n$, be sure to include initial values.
				\begin{solution}
				\begin{proof}
                    
                    Base Case: Showing the initial values up to $n = 4$:

                    For $n = 0$: $T_0 =1$

                    For $n = 1$: $T_1 =1$ (Using a single $1 \times 1$ tile)

                    For $n = 2$: $T_2 =2$ (Using either two $1 \times 1$ tiles or a single $1 \times 2$ tile)

                    For $n = 3$: $T_3 =3$ (Using either three $1 \times 1$ tiles, or a $1 \times 2$ tile and a $1 \times 1$ tile, in different orders)

                    For $n = 4$: $T_4 =5$ (Using either four $1 \times 1$ tiles, or a combination of $1 \times 2$ tiles and $1 \times 1$ tiles, or two $1 \times 2$ tiles)
                    \\\\
                    Induction Hypothesis: This relationship holds true for some $k$, that is $T_k = T_{k-1} + T_{k-2}$ for $k \geq 2$. In other words, the number of ways to perfectly tile a $1 \times n$ floor is equal to the sum of the two previous $n$'s tiling configurations.
                    \\\\
                    Induction Step: We must now show that this relationship continues to hold true for $k + 1$,
                    that is $T_{k+1} = T_{(k+1)-1} + T_{(k+1)-2}$ for $k \geq 2$.
                    \\\\
                    Simplifying the RHS:
                    
                    $T_{(k+1)-1} + T_{(k+1)-2}$

                    $T_{k} + T_{k-1}$
                    \\\\
                    Thus:

                    $T_{k+1} = T_{k} + T_{k-1}$
                    \\\\
                    Conclusion:

                    As shown in the base case, the relationship is true for $n = 2$, $n = 3$, and $n = 4$; and the 			relationship’s truth for $n = k \geq 2$ implies its truth for $n = k + 1$ and so the relationship is true for all nonnegative integers by the Principle of Mathematical Induction, proving the following formula:
                    \\\\
                    $T_n = T_{n-1} + T_{n-2}$ for $n \geq 2$
				\end{proof} 
				\end{solution}

				\part Please give a combinatorial proof of the following theorem. Note that the notation $\lfloor n/2 \rfloor$ is a way to round down to the nearest integer. 

				\begin{theorem}
					For every integer $n \ge 0$,
					\[
					T_{n} = \sum_{k=0}^{\lfloor n/2 \rfloor} \binom{n-k}{k}
					\]
				\end{theorem}

				\begin{solution}
				\begin{proof}


				
				\end{proof}

			\end{solution}

				\part Please prove the following theorem. 
				
				\begin{theorem}
					For every integer $n \ge 0$,
					\[
					T_{n+1} = 1+ \sum_{i=1}^n T_{i-1}
					\]
				\end{theorem}

				\begin{solution}
				\begin{proof}


				
				\end{proof}

			\end{solution}


			\end{parts}

			\question Please prove the following theorem. 
			
			\begin{theorem}
			For every $n \in \mathbb{Z}^+$, if any one square is removed from a $2^n \times 2^n$ chessboard, the result can be perfectly tiled with 
			\begin{tikzpicture}[scale=0.2]
			\draw[thick] (0,0) rectangle (1,1);
			\draw[thick] (1,0) rectangle (2,1);
			\draw[thick] (0,1) rectangle (1,2);
			\end{tikzpicture}
			--shaped tiles.
			\end{theorem}

			\begin{solution}
               \begin{proof}
        
      
                Claim: The Theorem can be proved through induction. 

                Base Case:

                n = 1

\begin{tikzpicture}[scale=0.8]
    % Bottom-left
    \filldraw[thick, fill=gray!40] (0,0) rectangle (1,1);
    % Bottom-right
    \filldraw[thick, fill=gray!40] (1,0) rectangle (2,1);
    % Top-left (removed square) with red cross
    \draw[thick] (0,1) rectangle (1,2);
    \draw[red, thick] (0,1) -- (1,2);
    \draw[red, thick] (0,2) -- (1,1);
    % Top-right
    \filldraw[thick, fill=gray!40] (1,1) rectangle (2,2);
\end{tikzpicture}

As demonstrated in the picture the Theorem works for the base case.

Hypothesis: Assume this holds for $2^{n + 1} \times 2^{n+ 1}$

Inductive Step:
For any of the $2^{n + 1} \times 2^{n+ 1}$ boards we can split them up into 4 sections which are each of the size $2^{n} \times 2^{n}$. After we do that we can put last L shaped tile in the center createing the base case. 

Each


\begin{tikzpicture}[scale=0.8]
    % 4x4 board: inner-corner square of each quadrant is gray; others light blue
    \foreach \x in {0,1,2,3} {
        \foreach \y in {0,1,2,3} {
            \ifnum\x=1
                \ifnum\y=2
                    \filldraw[thick, fill=gray!40] (\x,\y) rectangle (\x+1,\y+1);
                \else
                    \ifnum\y=1
                        \filldraw[thick, fill=gray!40] (\x,\y) rectangle (\x+1,\y+1);
                    \else
                        \filldraw[thick, fill=blue!20] (\x,\y) rectangle (\x+1,\y+1);
                    \fi
                \fi
            \else
                \ifnum\x=2
                    \ifnum\y=2
                        \filldraw[thick, fill=gray!40] (\x,\y) rectangle (\x+1,\y+1);
                    \else
                        \ifnum\y=1
                            \filldraw[thick, fill=gray!40] (\x,\y) rectangle (\x+1,\y+1);
                        \else
                            \filldraw[thick, fill=blue!20] (\x,\y) rectangle (\x+1,\y+1);
                        \fi
                    \fi
                \else
                    \filldraw[thick, fill=blue!20] (\x,\y) rectangle (\x+1,\y+1);
                \fi
            \fi
        }
    }
    % Darker outlines to show the four 3-square L-tiles (one per quadrant)
    \draw[black, ultra thick] (0,2) -- (0,4) -- (2,4) -- (2,3) -- (1,3) -- (1,2) -- cycle;
    \draw[black, ultra thick] (2,3) -- (2,4) -- (4,4) -- (4,2) -- (3,2) -- (3,3) -- cycle;
    \draw[black, ultra thick] (0,0) -- (0,2) -- (1,2) -- (1,1) -- (2,1) -- (2,0) -- cycle;
    \draw[black, ultra thick] (2,0) -- (2,1) -- (3,1) -- (3,2) -- (4,2) -- (4,0) -- cycle;
    % Dark outlines around the four 2x2 quadrants
    \draw[black, ultra thick] (0,2) rectangle (2,4);
    \draw[black, ultra thick] (2,2) rectangle (4,4);
    \draw[black, ultra thick] (0,0) rectangle (2,2);
    \draw[black, ultra thick] (2,0) rectangle (4,2);
    % Cross out the top-left square of the center 2x2
    \draw[red, ultra thick] (1,2) -- (2,3);
    \draw[red, ultra thick] (1,3) -- (2,2);
\end{tikzpicture}

example: n=2

Therefore through induction we can prove that for every value of n we can tile the floor perfectly.
                \end{proof}
			\end{solution}
		\end{questions}
	
\end{document}
